\newcommand{\jobtitle}{Versatile Frontend Developer (m/f)}
\newcommand{\aboutustitle}{About us}
\newcommand{\aboutuscontent}{%
We are a bunch of passionate developers, miracle workers, and transformers who have one mission: Build METRO’s 
Multi-Channel wholesale business of the future. We closely listen to our customers in order to build and continuously 
improve applications that cater their specific needs but are still highly scalable.\\[2ex]
Together with us you will build great user experience in an international and continuously evolving ecosystem of 
applications and services.\\[2ex]
Joining our team means experiencing a startup-like atmosphere while being part of an international market-leading 
company in retail. Indeed, METRO GROUP Wholesale \& Food Specialist Company operates in 35 countries, 
serves over 21 million customers and achieved sales of around €37 billion in 2015/2016. Moreover, we are an equal 
opportunity employer. We offer all qualified employees and applicants identical chances.
}
\newcommand{\joinustitle}{Join us}
\newcommand{\joinuscontent}{%
If you want to lead the digital revolution of wholesale business, get in touch with us:\\[3ex]
\contactdetails
}
\newcommand{\environmenttitle}{What you can expect}
\newcommand{\environmentcontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item Small agile teams consisting of product owners and developers as well as UI and UX designers.
\item A vital design expert community crafting UI components for multiple use cases and applications serving millions 
      of users from various countries.
\item A dynamic start-up-like environment where still many new projects and teams are forming and where you can 
      make an impact.
\item An open atmosphere and working culture where information and knowledge is exchanged and transformed into action.
\item A set of great tools to work with like a living style guide, UI pattern- and component libraries which you can 
      actively further shape and develop.
\item A team of passionate full stack developers loving high code quality and creating solutions in close exchange with 
      you.
\item A lot of fun, freedom for your own creativity and great people.
\end{itemize}
}
\newcommand{\profiletitle}{Your profile}
\newcommand{\profilecontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item Programming the UI of responsive web applications and optimally mobile apps is your daily job.
\item You love clean code and implementing innovative technologies is in your DNA.
\item You are continuously thriving to improve the products and services your team provides.
\item You gained experience in creating UI Pattern Libraries, CSS and style guides.
\item You have a strong design thinking and customer centric mindset.
\item You are a highly motivated team player with a self-organized way of working.
\item It is no hurdle for you to express yourself in English language.
\end{itemize}
}
\newcommand{\benefitstitle}{What we offer on top}
\newcommand{\benefitscontent}{%
a great team $\bullet$ flexible working time $\bullet$ home office $\bullet$ individual trainings $\bullet$ career 
improvement programs $\bullet$ support for child and home care $\bullet$ various health and sports programs $\bullet$ 
team events $\bullet$ free coffee $\bullet$ regular pizza parties
}

