\newcommand{\jobtitle}{Passionate Software Developer (m/f)}
\newcommand{\aboutustitle}{About us}
\newcommand{\aboutuscontent}{%
We are a bunch of passionate developers, designers, miracle workers, and transformers who have one mission: Build 
METRO’s Multi-Channel wholesale business of the future. Using the newest technologies, we develop and deploy more than 
150 microservices every day which are used to process millions of our customers’ requests and orders.\\[5ex]
Joining our team means experiencing a startup-like atmosphere while being part of an international market-leading 
company in retail. Indeed, METRO GROUP Wholesale \& Food Specialist Company operates in 35 countries, 
serves over 21 million customers and achieved sales of around €37 billion in 2015/2016. Moreover, we are an equal 
opportunity employer. We offer all qualified employees and applicants identical chances.
}
\newcommand{\joinustitle}{Join us}
\newcommand{\joinuscontent}{%
If you want to lead the digital revolution of wholesale business, get in touch with us:\\[3ex]
\contactdetails
}
\newcommand{\environmenttitle}{What you can expect}
\newcommand{\environmentcontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item You are involved in all phases of software engineering, from conception over implementation to testing and 
      delivery.
\item You work in small independent teams to develop customer-oriented services and applications.
\item An agile development environment with pair programming, code reviews, and continuous deployment.
\item A high working quality, ensured by extensive test automation.
\item A flexible use of innovative technologies.
\item A constant exchange of knowledge within your team, with our project managers/product owners, and external 
      partners.
\item An international work environment with colleagues from all over the world.
\end{itemize}
}
\newcommand{\profiletitle}{Your profile}
\newcommand{\profilecontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item You have profound knowledge in some programming language (of your choice).
\item You are eager to constantly learn new programming languages and technologies.
\item You have enthusiasm for automating and automatically scaling tests and deployments (with Docker and Kubernetes).
\item You are interested in splitting large projects into small, manageable subprojects with microservices.
\item You are already developing software ``full stack'' meaning from the front end over the back end to the 
      persistence layer or you want to learn how to do it.
\item You have fun solving complex problems and you want to work in a team that shares this ambition with you.
%\item 
\end{itemize}
\vspace*{-3mm}
Regardless whether you have already several years of professional experience or you come directly from the 
      university -- we have a position for you.\\
}
\newcommand{\benefitstitle}{What we offer on top}
\newcommand{\benefitscontent}{%
a great team $\bullet$ flexible working time $\bullet$ home office $\bullet$ individual trainings $\bullet$ career 
improvement programs $\bullet$ support for child and home care $\bullet$ various health and sports programs $\bullet$ 
team events $\bullet$ free coffee $\bullet$ regular pizza parties
}

