\newcommand{\jobtitle}{Visionary UI Designer (m/f)}
\newcommand{\aboutustitle}{About us}
\newcommand{\aboutuscontent}{%
We are a bunch of passionate developers, designers, miracle workers, and transformers who have one mission: Build 
METRO’s Multi-Channel wholesale business of the future. We closely listen to our customers in order to build and 
continuously improve applications that cater their specific needs but are still highly scalable.\\[2ex]
Together with us you will build great user experience in an international and continuously evolving ecosystem of 
applications and services.\\[2ex]
Joining our team means experiencing a startup-like atmosphere while being part of an international market-leading 
company in retail. Indeed, METRO GROUP Wholesale \& Food Specialist Company operates in 35 countries, 
serves over 21 million customers and achieved sales of around €37 billion in 2015/2016. Moreover, we are an equal 
opportunity employer. We offer all qualified employees and applicants identical chances.
}
\newcommand{\joinustitle}{Join us}
\newcommand{\joinuscontent}{%
If you want to lead the digital revolution of wholesale business, get in touch with us:\\[3ex]
\contactdetails
}
\newcommand{\environmenttitle}{What you can expect}
\newcommand{\environmentcontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item Small agile teams consisting of product owners and developers as well as UI and UX designers.
\item A vital design and UX expert community creating wireframes and screen designs for multiple use cases from various 
      countries.
\item A customer centric organization where user research and testing is recognized as a corner stone of every 
      development.
\item A dynamic start-up-like environment where still many new projects and teams are forming and where you can 
      make an impact.
\item An open atmosphere and working culture where information and knowledge is exchanged and transformed into action.
\item A set of great design tools to work with like a living style guide and UI pattern libraries, which you will 
      contribute to and shape.
\item A team of passionate UI and UX designers loving to exchange and learn from each other to build great user 
      experience.
\item A lot of fun, freedom for your own creativity and great people.
\end{itemize}
}
\newcommand{\profiletitle}{Your profile}
\newcommand{\profilecontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item You have a strong design thinking and customer oriented mindset.
\item You are a highly motivated team player, who is still eager to learn and has a self-organized way of working.
\item Understanding business people and talking to developers is no mystery for you.
\item You are continuously thriving to improve the products and services your team provides.
\item You are familiar with creating UI design principles and style guides.
\item Using design tools like Sketch, Adobe Photoshop, Adobe Illustrator or Invision is part of your daily work.
\item You have profound work experience in UI design.
\item It is no hurdle for you to express yourself in English language.
\end{itemize}
}
\newcommand{\benefitstitle}{What we offer on top}
\newcommand{\benefitscontent}{%
a great team $\bullet$ flexible working time $\bullet$ home office $\bullet$ individual trainings $\bullet$ career 
improvement programs $\bullet$ support for child and home care $\bullet$ various health and sports programs $\bullet$ 
team events $\bullet$ free coffee $\bullet$ regular pizza parties
}

