\newcommand{\jobtitle}{Scrum Master / Agile Coach (m/f)}
\newcommand{\aboutustitle}{About us}
\newcommand{\aboutuscontent}{%
We are a bunch of passionate developers, designers, miracle workers, and transformers who have one mission: Build 
METRO's Multi-Channel wholesale business of the future. We closely listen to our customers in order to build and 
continuously improve applications that cater their specific needs but are still highly scalable.\\[2ex]
Together with us you will build great user experience in an international and continuously evolving ecosystem of 
applications and services.\\[2ex]
Joining our team means experiencing a startup-like atmosphere while being part of an international market-leading 
company in retail. Indeed, METRO GROUP Wholesale \& Food Specialist Company operates in 35 countries, serves over 21 
million customers and achieved sales of around €37 billion in 2015/2016. Moreover, we are an equal opportunity 
employer. We offer all qualified employees and applicants identical chances.
}
\newcommand{\joinustitle}{Join us}
\newcommand{\joinuscontent}{%
If you want to lead the digital revolution of wholesale business, get in touch with us:\\[3ex]
\contactdetails
}
\newcommand{\environmenttitle}{What you can expect}
\newcommand{\environmentcontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item You will analyze and guide an enterprise wide software engineering process, from conception through programming, 
      testing and delivery.
\item You will help teams to understand and measure what customer value means.
\item You will improve the process of developing customer-oriented services and applications in short release cycles.
\item You will divide an agile transformation roadmap into iterative \& incremental pieces that constantly drive change.
%\item You will work in an environment having the atmosphere and freedom of a startup and the stability and impact of a 
%      big company.
\item You will work with smart colleagues from all over the world and you can expect a challenging environment that 
      demands all your skills in the transformation process towards an agile organization.
\end{itemize}
}
\newcommand{\profiletitle}{Your profile}
\newcommand{\profilecontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
%\item You have a Bachelor's or Master's degree in Computer Science, Physics, Mathematics or a comparable academic 
%      education.
\item You have profound knowledge in Scrum, Kanban, and a combination of both.
\item You have profound work experience in how to scale agile in an enterprise organization.
\item You have already built your own toolbox of agile good practices ready to be used with the teams.
\item You are a team player who wants to continuously learn and advance your professional skills.
\item You are highly motivated to contribute to the transformation of our company.
\item It is no hurdle for you to express yourself in English language.
\end{itemize}
}
\newcommand{\benefitstitle}{What we offer on top}
\newcommand{\benefitscontent}{%
a great team $\bullet$ flexible working time $\bullet$ home office $\bullet$ individual trainings $\bullet$ career 
improvement programs $\bullet$ support for child and home care $\bullet$ various health and sports programs $\bullet$ 
team events $\bullet$ free coffee $\bullet$ regular pizza parties
}

