\newcommand{\jobtitle}{Passionate Sitecore Developer (m/f)}
\newcommand{\aboutustitle}{\defaultaboutustitleEN}
\newcommand{\aboutuscontent}{%
We are a bunch of passionate developers, designers, miracle workers, and transformers who have one mission: Build 
METRO’s Multi-Channel wholesale business of the future. Using the newest technologies, we provide solutions for a multi 
data center and high availability environment. We are driving the evolution of the digital communication platform that 
will be seen by more than 15 million visitors per month.\\[5ex]
\defaultaboutuscontentjoiningEN
}
\newcommand{\joinustitle}{\defaultjoinustitleEN}
\newcommand{\joinuscontent}{%
\defaultjoinuscontentEN
\contactdetailspascal
}
\newcommand{\environmenttitle}{\defaultenvironmenttitleEN}
\newcommand{\environmentcontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item An agile development environment with pair programming and code reviews.
\item You are involved in all phases of software engineering, from conception over implementation to testing and 
      delivery.
\item A strong focus on collaboration, people, and self organization.
\item An international work environment with colleagues from all over the world.
\item You work in small independent teams to develop customer-oriented services and applications.
\item A flexible use of innovative technologies.
\item A constant exchange of knowledge within your team and other members of the organization.
\item Freedom for own ideas and a ``never stop'' learning culture.
\end{itemize}
}
\newcommand{\profiletitle}{\defaultprofiletitleEN}
\newcommand{\profilecontent}{%
\vspace*{-4mm}
\begin{itemize}[noitemsep]
\item You have comprehensive experience in developing CMS based web applications (ideally with Sitecore).
\item You have profound development knowledge of the C\# .NET technology stack.
\item You are familiar with REST, JSON, HTML, CSS, CSS Frameworks like Bootstrap, and JavaScript.
\item Ideally you have experience with Sitecore 8.x, TDS, SOLR, Sitecore Rocks, Unit Testing, and Front-End Testing.
\item You are eager to constantly learn new technologies.
\item You have enthusiasm for automating and automatically scaling tests and deployments.
\item You are already developing software ``full stack'' meaning from the front end over the back end to the 
      persistence layer or you want to learn how to do it.
\item You have fun solving complex problems and you want to work in a team that shares this ambition with you.
\item You have experience with agile development methodologies.
\end{itemize}
}
\newcommand{\benefitstitle}{\defaultbenefitstitleEN}
\newcommand{\benefitscontent}{\defaultbenefitscontentEN}

